---
title: "prior_plot"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ">"
)
```

```{r setup}
library(saferGraph)
```
<br>

### Argument param.reinitial
```{r}
pdf("file_plot")
prior_plot(param.reinitial = FALSE)
```
<br>

### Argument xlog.scale
```{r}
pdf("file_plot")
prior_plot(xlog.scale = TRUE)
```
<br>

### Argument ylog.scale
```{r}
pdf("file_plot")
prior_plot(ylog.scale = TRUE)
```
<br>

### Argument remove.label
```{r}
pdf("file_plot")
prior_plot(remove.label = FALSE)
```
<br>

### Argument remove.x.axis
```{r}
pdf("file_plot")
prior_plot(remove.x.axis = FALSE)
```
<br>

### Argument remove.y.axis
```{r}
pdf("file_plot")
prior_plot(remove.y.axis = FALSE)
```
<br>

### Argument std.x.range
```{r}
pdf("file_plot")
prior_plot(std.x.range = FALSE)
```
<br>

### Argument std.y.range
```{r}
pdf("file_plot")
prior_plot(std.y.range = FALSE)
```
<br>

### Argument down.space
```{r}
pdf("file_plot")
prior_plot(down.space = 2)
```
<br>

### Argument left.space
```{r}
pdf("file_plot")
prior_plot(left.space = 2)
```
<br>

### Argument up.space
```{r}
pdf("file_plot")
prior_plot(up.space = 2)
```
<br>

### Argument right.space
```{r}
pdf("file_plot")
prior_plot(right.space = 2)
```
<br>

### Argument orient
```{r}
pdf("file_plot")
prior_plot(orient = 2)
```
<br>

### Argument dist.legend
```{r}
pdf("file_plot")
prior_plot(dist.legend = 5)
```
<br>

### Argument tick.length
```{r}
pdf("file_plot")
prior_plot(tick.length = 1)
```
<br>

### Argument box.type
```{r}
pdf("file_plot")
prior_plot(box.type = "l")
```
<br>

### Argument amplif.label
```{r}
pdf("file_plot")
prior_plot(amplif.label = 1.5)
```
<br>

### Argument amplif.axis
```{r}
pdf("file_plot")
prior_plot(amplif.axis = 1.5)
```
<br>

### Argument display.extend
```{r}
pdf("file_plot")
prior_plot(display.extend = TRUE)
```
<br>

### Argument return.par
```{r}
pdf("file_plot")
prior_plot(return.par = TRUE)
```
<br>

### Argument safer_check
```{r}
pdf("file_plot")
prior_plot(safer_check = TRUE)
```
<br>

### All the arguments
```{r, echo = TRUE, error = TRUE}
pdf("file_plot")
prior_plot(
  param.reinitial = TRUE, 
  xlog.scale = TRUE, 
  ylog.scale = TRUE, 
  remove.label = FALSE, 
  remove.x.axis = FALSE, 
  remove.y.axis = FALSE, 
  std.x.range = FALSE, 
  std.y.range = FALSE, 
  down.space = 2, 
  left.space = 2, 
  up.space = 2, 
  right.space = 2, 
  orient = 2, 
  dist.legend = 5, 
  tick.length = 1, 
  box.type = "l", 
  amplif.label = 1.5, 
  amplif.axis = 1.5, 
  display.extend = TRUE, 
  return.par = TRUE,
  safer_check = TRUE)
```
<br>